The unequal distribution of access to education and transport: insights from the São Paulo Metropolitan Region

### 2017-04-02 paper_v2.tex
Improve discussion of Ingram (1971)

The first well-known attempt to define accessibility quantitatively was by Ingram (1971), which presented a range of measures related to
distance (Euclidean and network), barriers and different functions
representing distance decay. This early work made the distinction
between accessibility indices that apply to zones or single `desire
lines': ``relative accessibility is defined as a measure of the effort of overcoming spatial separation between two points, while the integral accessibility is defined as a measure of the effort of overcoming spatial separation between a point and all other points within an area'' (Allen, Liu, and Singer 1993). In subsequent works, the measurement of job accessibility by particular transport modes has received vast attention in the literature (Geurs and Van Wee 2004), while studies on access to education has largely focused on the consequences of mode choice on socio-economic indicators and school outcomes (see for instance Asahi (2014), Falch, Lujala, and Str{ø}m (2013) and Dickerson and McIntosh (2012) on the impact of accessibility on school outcomes, and Andersson, Malmberg, and {Ö}sth (2012) and Easton and Ferrari (2015) on the effect of changes in travel-to-school patterns in developed economies).

>>>>

The first well-known quantitative definition of accessibility was by Ingram (1971).
This seminal paper presented a range of measures determined by
distances to destinations (Euclidean and network), natural barriers and 
distance decay functions. This early work made the distinction
between accessibility indices that apply to zones or single `desire
lines': ``relative accessibility is defined as a measure of the effort of overcoming spatial separation between two points, while the integral accessibility is defined as a measure of the effort of overcoming spatial separation between a point and all other points within an area'' (Allen, Liu, and Singer 1993). In subsequent works, the measurement of job accessibility by particular transport modes has received vast attention in the literature (Geurs and Van Wee 2004), while studies on access to education has largely focused on the consequences of mode choice on socio-economic indicators and school outcomes (see for instance Asahi (2014), Falch, Lujala, and Str{ø}m (2013) and Dickerson and McIntosh (2012) on the impact of accessibility on school outcomes, and Andersson, Malmberg, and {Ö}sth (2012) and Easton and Ferrari (2015) on the effect of changes in travel-to-school patterns in developed economies).
